### 2022-07-25 paper/localpsf.tex
more paper edits. Barely under 25 pages

Algorithm \ref{alg:varhpi_mean_cov} from Section \ref{sec:intromoments} allows us to compute $\spatialvol$, $\spatialmean$, and $\spatialcov$ by applying $\Aop^T$ to a small number of polynomial functions, and \eqref{eq:support_ellipsoid} uses $\spatialvol$, $\spatialmean$, and $\spatialcov$ to form an ellipsoid shaped estimate for the support of $\phi_x$, \emph{without} computing $\phi_x$. This allows us to compute large numbers of impulse responses, $\impulseresponse_{x_i}$, in ``batches,'' $\eta_b$ (see Figure \ref{fig:batches_intro}). We compute the impulse response batch $\eta_b$ by applying $\Aop$ to a weighted sum of point sources (Dirac comb) associated with a batch, $S_b$, of points $x_i$ scattered throughout $\Omega$ (Section \ref{sec:get_impulse_response}). The batch of points $S_b$ is chosen via a greedy ellipsoid packing algorithm so that, for $x_i,x_j \in S_b$, the support of $\impulseresponse_{x_i}$ and the support of $\impulseresponse_{x_j}$ do not overlap (or do not overlap much) if $i \neq j$ (Section \ref{sec:sample_point_selection}). Because these supports do not overlap, we can post-process $\eta_b$ to recover the functions $\impulseresponse_{x_i}$ associated with all points $x_i \in S_b$---with one application of $\Aop$, we recover many $\impulseresponse_{x_i}$ (Section \ref{sec:get_impulse_response}). The process is repeated to get more batches, until a desired number of impulse responses is reached.

@@

We use the framework described in this paper to generate Hessian preconditioners. We build H-matrix approximations of the data-misfit Gauss-Newton Hessian (the term in $H_\text{gn}$ that arises from the data misfit) using 1, 5, and 25 impulse responses batches. The resulting H-matrices, which may be indefinite due to approximation error, are modified to be symmetric positive definite via the procedure described in Appendix \ref{sec:make_spd}, with $l=2$. We approximate $H_\text{gn}$ rather than $H$ because $H$ often has negative values in its integral kernel when one is away from the optimal point. Our results show that our preconditioners are also good preconditioners for $H$. The H-matrix approximation of data misfit Gauss-Newton Hessian is added to a H-matrix approximation of the Hessian of the regularization term, $J_r$, to form a H-matrix approximation of the Gauss-Newton Hessian. For the Hessian of the regularization term, straightforward calculation shows that the discrete regularization term in both the Hessian and the Gauss-Newton Hessian is given by
$
(\gamma \bm{K} + \delta \bm{M}) \bm{M}^{-1} (\gamma \bm{K} + \delta \bm{M})
$
where $\bm{K}$ is a finite element stiffness matrix with appropriate boundary conditions, and $\bm{M}$ is the finite element mass matrix. These matrices are sparse, so we form H-matrix representations of these matrices using standard sparse H-matrix techniques. Then we invert $\bm{M}^{-1}$, and multiply these matrices together using H-matrix methods. We factor the overall Gauss-Newton Hessian approximation, denoted $\widetilde{H}$, using fast H-matrix methods, then and use the factorization as a preconditioner \cite{HLIBPRO}. The resulting preconditioners for 1, 5, and 25 impulse response batches are denoted by PSF (1), PSF (5), and PSF (25), respectively.

>>>>

Section \ref{sec:intromoments} allows us to compute $\spatialvol$, $\spatialmean$, and $\spatialcov$ by applying $\Aop^T$ to a small number of polynomial functions, and \eqref{eq:support_ellipsoid} uses $\spatialvol$, $\spatialmean$, and $\spatialcov$ to form an ellipsoid shaped estimate for the support of $\phi_x$, \emph{without} computing $\phi_x$. This allows us to compute large numbers of impulse responses, $\impulseresponse_{x_i}$, in ``batches,'' $\eta_b$ (see Figure \ref{fig:batches_intro}). We compute the impulse response batch $\eta_b$ by applying $\Aop$ to a weighted sum of point sources (Dirac comb) associated with a batch, $S_b$, of points $x_i$ scattered throughout $\Omega$ (Section \ref{sec:get_impulse_response}). The batch of points $S_b$ is chosen via a greedy ellipsoid packing algorithm so that, for $x_i,x_j \in S_b$, the support of $\impulseresponse_{x_i}$ and the support of $\impulseresponse_{x_j}$ do not overlap (or do not overlap much) if $i \neq j$ (Section \ref{sec:sample_point_selection}). Because these supports do not overlap, we can post-process $\eta_b$ to recover the functions $\impulseresponse_{x_i}$ associated with all points $x_i \in S_b$---with one application of $\Aop$, we recover many $\impulseresponse_{x_i}$ (Section \ref{sec:get_impulse_response}). The process is repeated to get more batches, until a desired number of impulse responses is reached.

@@

We use the framework described in this paper to generate Hessian preconditioners. We build H-matrix approximations of the data-misfit Gauss-Newton Hessian (the term in $H_\text{gn}$ that arises from the data misfit) using 1, 5, and 25 impulse responses batches. The resulting H-matrices, which may be indefinite due to approximation error, are modified to be symmetric positive definite via the procedure described in Appendix \ref{sec:make_spd}, with $l=2$. We approximate $H_\text{gn}$ rather than $H$ because $H$ often has negative values in its integral kernel when one is away from the optimal point. Our results show that our preconditioners are also good preconditioners for $H$. The H-matrix approximation of data misfit Gauss-Newton Hessian is added to a H-matrix approximation of the Hessian of the regularization term, $J_r$, to form a H-matrix approximation of the Gauss-Newton Hessian. For the Hessian of the regularization term, straightforward calculation shows that the discrete regularization term in both the Hessian and the Gauss-Newton Hessian is given by
$
(\gamma \bm{K} + \delta \bm{M}) \bm{M}^{-1} (\gamma \bm{K} + \delta \bm{M})
$
where $\bm{K}$ is a finite element stiffness matrix with appropriate boundary conditions, and $\bm{M}$ is the finite element mass matrix. These matrices are sparse, so we form H-matrix representations of these matrices using standard sparse H-matrix techniques. Then we invert $\bm{M}^{-1}$, and multiply these matrices together using H-matrix methods. We factor the overall Gauss-Newton Hessian approximation, denoted $\widetilde{H}$, using fast H-matrix methods, then and use the factorization as a preconditioner \cite{HLIBPRO}. The approximations for 1, 5, and 25 impulse response batches are denoted by PSF (1), PSF (5), and PSF (25), respectively.
